### 2016-11-04 paper/evaluation.tex
Updated eval section

\newcommand{\RQB}{What is the distribution of CPU and IO bound
regression tests from the sample set?}

@@

\newcommand{\RQD}{How often developers use the parallelism features
from build manager systems to improve performance on test execution?}

@@

The first research question addresses the distribution of subjects per
time cost. We are interested on identifying time-consuming test suites
to investigate further their characteristics (\eg, type of application
and bottlenecks from execution) \Jbc{do we have a better arguments?}.
The second research question addresses the distribution of execution
time per test case. For each subject identified in the first research
question, we are interested in understanding how balanced is the cost
of the test suite in contrast to the cost of test cases and if there
are subjects where the time cost is mostly dominated by a small
fraction of test cases.

@@

To evaluate the distribution of execution time, we calculated the cost
from 90\% of test cases ordered by execution time and compared the
resulting value to the total time.  We collected the elapsed time from
test cases for each generated report. Maven Surefire generates an XML
report with execution information (\eg, number of skipped tests and
elapsed time) per test suite \Jbc{Should I use the previous sentence
as a footnote or should I delete it?}. We noticed that some test cases
reported an elapsed time of zero: since the reported time is in
milliseconds, some tests may execute in a shorter time. \Fix{..to be
continued...}

@@

To evaluate the distribution of CPU and IO bound in regression tests
from the sample set, we proposed the definition of \emph{cpuness}
computed as the follow: $((user\_t + system\_t) / elapsed\_t) * 100$,
where \emph{user\_t} is the elapsed time of execution in \emph{user
mode}, \emph{system\_t} is the elapsed in \emph{kernel mode}, and
\emph{elapsed\_t} is the elapsed time to finish the execution. We
measured the \emph{cpuness} of each regression test \Fix{...elaborate
the meaning of cpuness} \Fix{Describe how I measured user, system and
"wall" time}.  \Fix{Explain results}.  \Fix{show plots}

@@

%% \begin{itemize}
%%     \item \RQFOUR
%% \end{itemize}

>>>>

\newcommand{\RQB}{What is the distribution of CPU and IO bound
regression test suites from the sample set?}

@@

\newcommand{\RQD}{How often developers use the parallelism features
from build systems to improve runtime performance?}

@@

The first research question addresses the distribution of subjects per
time cost. We are interested on identifying time-consuming test suites
to investigate further their characteristics (\eg, type of application
and bottlenecks from execution) \Jbc{do we have more arguments?}.  The
second research question addresses the distribution of execution time
per test case. For each subject identified in the first research
question, we investigate how balanced is the cost of the test suite in
contrast to the cost of test cases and if there are subjects where the
time cost is mostly dominated by a small fraction of test cases. The
third research question addresses the distribution of regression tests
according to the use of computational resources. We are interested in
investigating if regression test suites are CPU intensive and if there
are opportunities to improve performance. The RQ4 addresses
\Fix{...elaborate...}

@@

To evaluate the distribution of execution time per project, we sorted
the test cases by increasing order of elapsed time and calculated the
number of tests executed in 90\% of the total time. Later, we reported
the \Fix{balance} of execution time by dividing the number of tests
that represents 90\% of the execution time by the number of tests
cases. For instance, a balance of 50\% indicates \Fix{...}.  \Fix{We
collected the elapsed time from test cases for each generated report.
Maven Surefire generates an XML report with execution information
(\eg, number of skipped tests and elapsed time) per test suite
\Jbc{Should I use the previous sentence as a footnote or should I
delete it?}. We noticed that some test cases reported an elapsed time
of zero: since the reported time is in milliseconds, some tests may
execute in a shorter time. \Fix{..to be continued...}}. Results
indicate that \Fix{...}.

@@

To evaluate the distribution of CPU and IO intensive test suites from
the sample set, we used the command \emph{sar} to monitor the system
activity in background while tests ran. \emph{Sar} is a command that
collects and reports statistics (\eg, percentage of IO waiting and
usage of CPU in user mode) based on the kernel activity and it is
highly configurable to collect detailed information (\eg, usage of a
specific processor core or percentage of network interface
utilization). We configured \emph{sar} to report \Fix{...explain how
we executed and what fields we are interested}. \Fix{explain fields}.
Figure \Fix{A} shows the distribution of subjects grouped in intervals
of \Fix{W}\% of CPU utilization. Results indicates that \Fix{...}

\Comment{we proposed the definition of \emph{cpuness}
computed as the follow: $((user\_t + system\_t) / elapsed\_t) * 100$,
where \emph{user\_t} is the elapsed time of execution in \emph{user
mode}, \emph{system\_t} is the elapsed in \emph{kernel mode}, and
\emph{elapsed\_t} is the elapsed time to finish the execution. We
measured the \emph{cpuness} of each regression test \Fix{...elaborate
the meaning of cpuness} \Fix{Describe how I measured user, system and
"wall" time}.  \Fix{Explain results}.  \Fix{show plots}}

@@

\begin{itemize}
    \item \RQD
\end{itemize}
